	\documentclass[twoside]{article}
\usepackage{estilo-ejercicios}
\setcounter{section}{0}
\newtheorem{defin}{Definition}[section]
\newtheorem{lem}[defin]{Lemma}
\newtheorem{propo}[defin]{Proposition}
\newtheorem{thm}[defin]{Theorem}
\newtheorem{eje}[defin]{Example}
\newtheorem{obs}[defin]{Observación}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
\renewcommand{\baselinestretch}{1,3}

\usepackage{empheq}
\newcommand*\widefbox[1]{\fbox{\hspace{2em}#1\hspace{2em}}}
\usepackage{cleveref}

\crefname{defin}{Definition}{definition}
%--------------------------------------------------------
\begin{document}

\title{Table of enriched categories}
\author{Javier Aguilar Martín}
\maketitle

\section{Summary table}
I may change the distribution to put all underlines together or each category folled by its underlined (enriched) version. Maybe full subcategories (including bounded categories) should go on a different table where I specify the supercategory. Also the alternatively enriched (mathpzc and mathcal font) categories could go on a different table where I specify where they are enriched over. There are several $\delta$ defined depending  on the enrichment used, possibly specify (writing the number of the definition, actually do this for all of them even if they are not repeated) which is one in case it is confusing.


\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Category} & \textbf{Objects} & \textbf{Morphisms} & \textbf{Monoidal structure}\\
\hline
$\mathrm{C}_R$ & Cochain complexes & Maps complexes & The usual one\\
\hline
$\mathrm{fC}_R$ & Filtered complexes & Maps of filtered complexes & $\Ima(F_iA ⊗ F_jB → A ⊗ B)$ \\
(\cref{filteredcomplex}) & & &(\cref{filteredtensor}) \\
\hline
$\mathrm{bgMod}_R$ & Bigraded modules & Maps of bidegree $(0,0)$& $(A ⊗ B)^j_i :=\bigoplus_{p,q}A^q_p ⊗ B^{j−q}_{i−p}$\\
\hline
$\mathrm{vbC}_R$ & Vertical bicomplexes & Maps of bigraded modules& As in $\bgmod$  and \\
        (\cref{vbC})         &           & that commute with differential & $d^{A⊗B} := d^A ⊗ 1 + 1 ⊗ d^B$\\ 
\hline
$\underline{\mathrm{C}_R}$ & Chain complexes & Maps of chain complexes with & Same as $\mathrm{C}_R$\\
                           &                 &  differential $\delta$ (\cref{delta1})&\\
\hline
$\underline{\mathrm{bgMod}_R}$ & Bigraded modules & Maps of any bidegree & Same as $\mathrm{bgMod}_R$\\
& & &\\
\hline
$\underline{\mathrm{vbC}_R}$ & Vertical bicomplexes & Maps of any bidegree with & Same as $\mathrm{vbC}_R$\\
                             &                      &  differential $\delta$ (\cref{delta1})&\\
\hline
$\mathrm{tC}_R$ & Twisted complexes & Maps of twisted complexes & (\cref{tensortwisted}) \\
& (\cref{twistedcomplex}) & (\cref{twistedmorphisms}) &\\
\hline
$\underline{\mathrm{tC}_R}$ & Twisted complexes & Maps of twisted complexes with& Same as $\mathrm{tC}_R$\\
& & differentials $d_i$ (\cref{di})&\\
\hline
$\mathrm{sfC}_R$ & Split filtered complexes & Maps of filtered complexes & Same as $\fc$ \\
(\cref{splitcomplex})& & (same as $\fc$)& \\
\hline
$\underline{\mathpzc{bgMod}_R}$ & Bigraded modules &$\underline{\mathpzc{bgMod}_R}(A,B)^v_u :=\prod_{j≥0}[A,B]^{v−j}_{u−j}$& $\widehat{\otimes}$ (\cref{tensorenriched}\\
(\cref{ubgMod})& & (Bigraded module \cref{weirdenrichment}) &\\
\hline
$\underline{t\mathcal{C}_R}$& Twisted complexes & $\utC(A,B)=(\underline{\mathpzc{bgMod}_R}(A,B),\delta)$ & $\widehat{\otimes}$ (\cref{tensorenriched})\\
(\cref{utC})& & (Vertical bicomplex \cref{delta2}) & \\
\hline
$\ufMod$ & Filtered modules & Bigraded module $\ufMod(K,L)$ & $\widehat{\otimes}$ (\cref{tensorenriched2})\\
(\cref{ufMod})& & & \\
\hline
$\ufC$ & Filtered complexes & Vertical bicomplex $\ufC(K,L)$ & $\widehat{\otimes}$ (\cref{tensorenriched2}) \\
(\cref{ufC}) & & (\cref{fmoddifferential})  & \\
 \hline
 $\usfC$ & Split filtered complex & Same as $\ufC$ & \\
\end{tabular}

Bonus: $\mathrm{bgMod}^\infty_R$ is the full subcategory of $\mathrm{tC}_R$ whose objects have $d_m=0$ for all $m$.

Bonus:$\usfMod$ the full subcategory of $\ufMod$ whose objects are split filtered modules.

Maybe leave the split ones as a bonus as well. 

Definitionn 3.10 for bounded subcategories. 

Diagram before section 3.3 can be useful

Endomorphism operad?

If I find some notation confusing because the same is used for different things I may use other notations at some point.
\section{Definitions}

Create a custom ennviroment to use the numbering of Sarah's paper for better identification \url{https://tex.stackexchange.com/questions/53978/custom-theorem-numbering}

Definition 2.2
\begin{defin}[Filtered $R$-module and morphisms]
A \emph{filtered $R$-module} $(A, F)$ is given by a family of $R$-modules $\{F_pA\}_{p∈\Z}$ indexed by the integers such that $F_{p−1}A ⊆ F_pA$ for all $p ∈ \Z$ and $A = ∪F_pA$. A morphism of filtered modules is a
morphism $f : A → B$ of $R$-modules which is compatible with filtrations: \[f(F_pA) ⊂ F_pB\text{ for all }p ∈ \Z.\]
\end{defin}

Definitions 2.4 and 2.5
\begin{defin}[Filtered complexes and morphism]\label{filteredcomplex}
A \emph{filtered complex} $(K, d, F)$ is a complex $(K, d) ∈ \mathrm{C}_R$ together with a filtration $F$ of each $R$-module $K^n$ such that $d(F_pK^n) ⊂ F_pK^{n+1}$ for all $p, n ∈ \Z$. Its morphisms are given by
morphisms of complexes $f : K → L$ compatible with filtrations: \[f(F_pK) ⊂ F_pL\text{ for all }p ∈ \Z.\]
\end{defin}

Definition 2.3
\begin{defin}\label{filteredtensor}
The tensor product of two filtered $R$-modules $(A, F)$ and $(B, F)$ is a filtered $R$-module,
with
 \[F_p(A ⊗ B) :=\sum_{i+j=p}\Ima(F_iA ⊗ F_jB → A ⊗ B).\]
This makes the category of filtered $R$-modules into a symmetric monoidal category, where the unit is given by $R$ with the trivial filtration $0 = F_{−1}R ⊂ F_0R = R$.
\end{defin}

Definition 2.7
\begin{defin}[Vertical bicomplexes and morphisms]\label{vbC}
A \emph{vertical bicomplex} is a bigraded $R$-module $A$ equipped with a vertical differential $d_A : A → A$ of bidegree $(0, 1)$. A morphism of vertical bicomplexes is a morphism of bigraded modules
of bidegree $(0, 0)$ commuting with the vertical differential.

The tensor product of two vertical bicomplexes $A$ and $B$ is given by endowing the tensor product of underlying bigraded modules with
vertical differential \[d^{A⊗B} := d^A ⊗ 1 + 1 ⊗ d^B : (A ⊗ B)^v_u → (A ⊗ B)^{v+1}_u.\]
\end{defin}


Definition 2.8
\begin{defin}[Enrichment over complexes]\label{delta1}
Let $A,B$ be bigraded modules. We define $[A,B]^∗_∗$
to be the bigraded module of morphisms of bigraded modules $A → B$. Furthermore, if $A,B$ are vertical bicomplexes, and $f ∈
[A,B]^v_u$, we define
\[δ(f) := d_Bf − (−1)^vfd_A.\]
\end{defin}

Definition 3.1
\begin{defin}[Twisted complexes]\label{twistedcomplex} A \emph{twisted complex} $(A, d_m)$ is a bigraded $R$-module $A = \{A^j_i \}$ together with a family
of morphisms $\{d_m : A → A\}_{m≥0}$ of bidegree $(−m,−m + 1)$ such that for all $m ≥ 0$,
\[\sum_{i+j=m}(−1)^id_id_j = 0.\]
\end{defin}

Definition 3.2
\begin{defin}[Morphisms of twisted complexes]\label{twistedmorphisms}
A morphism of twisted complexes $f : (A, d^A_m) → (B, d^B_m)$ is given by a family of morphisms of $R$-modules $\{f_m : A → B\}_{m≥0}$ of bidegree $(−m,−m)$ such that for all $m ≥ 0$,
\[\sum_{i+j=m}d^B_if_j =\sum_{i+j=m}(−1)^if_id^A_j.\]
The composition of morphisms is given by $(g \circ f)_m :=\sum_{i+j=m} g_if_j$.
\end{defin}


Lemma 3.3
\begin{defin}\label{tensortwisted}
The category $(\tc,⊗,R)$ is symmetric monoidal, where the monoidal structure is given
by the bifunctor
\[⊗ : \tc × \tc → \tc\]
which on objects is given by $((A, d^A_m), (B, d^B_m)) → (A ⊗ B, d^A_m ⊗ 1 + 1 ⊗ d^B_m)$ and on morphisms is
given by $(f, g) → f ⊗ g$, where $(f ⊗ g)_m :=\sum_{i+j=m} f_i ⊗ g_j$.
\end{defin}

Lemma 3.4
\begin{defin}[Enrichment over twisted complexes]\label{di} Let $A,B$ be twisted complexes. For $f ∈ [A,B]^v_u$, setting
\[(d_if) := (−1)^{i(u+v)}d^B_if − (−1)^vfd^A_i,\]
for $i ≥ 0$, endows $[A,B]^∗_∗$ with the structure of a twisted complex.
\end{defin}

%I will probably use direct sum totalization, whih has a specific notation and name in the paper, but I think the results for this totalization applies to the direct sum version (totalization with compact support).

Definition 3.6
\begin{defin}[Totalization and column filtration]
The total graded $R$-module $\mathrm{Tot}(A)$ of a bigraded $R$-module $A =\{A^j_i \}$ is given by
\[\mathrm{Tot}(A)^n :=\prod_{i≤0}A^{n+i}_i ⊕\bigoplus_{i>0}A^{n+i}_i .\]
The \emph{column filtration} of $\mathrm{Tot}(A)$ is the filtration given by \[F_p\mathrm{Tot}(A)^n :=\prod_{i≤p} A^{n+i}_i\text{ for all }p, n ∈ \Z.\]
\end{defin}

I should include the differential and Tot(f) here

This one comes much later but I prefer it to be here. It is possible to omit the filtration (but would have to check what consequences it has).

Definition 4.13
\begin{defin}
The \emph{totalization with compact support} of a vertical bicomplex $A$ is the filtered complex given by
\[\mathrm{Tot}_c(A)^n :=\sum_{i∈\Z}A^{n+i}_i\]
with the column filtration and with differential as for the totalization functor.

Given a morphism of vertical bicomplexes $f : A → B$ we get a morphism of filtered complexes $\mathrm{Tot}_c(f) : \mathrm{Tot}_c(A) → \mathrm{Tot}_c(B)$
constructed analogously to $\mathrm{Tot}(f)$.
\end{defin}

Definition 3.7
\begin{defin}[Split (filtered) complexes]\label{splitcomplex}
A filtered complex $(K, d, F)$ is said to be \emph{split} if $K = \mathrm{Tot}(A)$ is the total graded module of a bigraded $R$-module $A = \{A^j_i \}$ and $F$ is the column filtration of $\mathrm{Tot}(A)$.
\end{defin}

Definition 3.32
\begin{defin}[Weird enrichment]\label{weirdenrichment}
Let $A,B,C$ be bigraded modules. We denote by $\underline{\mathpzc{bgMod}_R}(A,B)$ the bigraded module given by
\[\underline{\mathpzc{bgMod}_R}(A,B)^v_u :=\prod_{j≥0}[A,B]^{v−j}_{u−j}\]
where $[A,B]$ is the inner hom-object of bigraded modules. More precisely, $g ∈ \underline{\mathpzc{bgMod}_R}(A,B)^v_u$ is given
by $g := (g_0, g_1, g_2, \dots )$, where $g_j : A → B$ is a map of bigraded modules of bidegree $(u − j, v − j)$.

Moreover, we define a composition morphism
\[c : \underline{\mathpzc{bgMod}_R}(B,C) ⊗ \underline{\mathpzc{bgMod}_R}(A,B) → \underline{\mathpzc{bgMod}_R}(A,C)\]
by
\[c(f, g)_m :=\sum_{i+j=m}(−1)^{i|g|}f_ig_j .\]
\end{defin}
Try to find a conceptual explanation of the sign in the above composition map.

Definition 4.17
\begin{defin}\label{delta2}
Let $(A, d^A_i), (B, d^B_i)$ be twisted complexes, $f ∈ \underline{\mathpzc{bgMod}_R}(A,B)^v_u$ and consider $d^A :=(d^A_i)_i ∈ \underline{\mathpzc{bgMod}_R}(A,A)^1_0$
and $d^B := (d^B_i)_i ∈ \underline{\mathpzc{bgMod}_R}(B,B)^1_0$. We define
\[δ(f) := c(d^B, f) − (−1)^{\langle f,d^A\rangle}c(f, d^A) ∈ \underline{\mathpzc{bgMod}_R}(A,B)^{v+1}_u\]
where $\langle f, d^A\rangle$ is the scalar product for the bidegrees and $c$ is the composition morphism described in Definition 3.32. More precisely,
\[(δ(f))_m :=\sum_{i+j=m}(−1)^{i|f|}d^B_if_j − (−1)^{v+i}f_id^A_j.\]
\end{defin}
Lemma 4.18? (in results obvsly)

Definition 4.19
\begin{defin}[Twisted complex weird enrichment]
For $A,B$ twisted complexes, we define $\underline{t\mathcal{C}_R}(A,B)$ to be the vertical bicomplex
$\underline{t\mathcal{C}_R}(A,B) := (\underline{\mathpzc{bgMod}_R}(A,B), δ)$.
\end{defin}

Definition 4.23
\begin{defin}\label{utC}
The $\vbc$-enriched category of twisted complexes $\utC$ is the enriched category given by the following data.
\begin{enumerate}[(1)]
\item The objects of $\utC$ are twisted complexes.
\item For $A,B$ twisted complexes the hom-object is the vertical bicomplex $\utC(A,B)$.
\item The composition morphism $c : \utC(B,C)⊗\utC(A,B) → \utC(A,C)$ is given by Definition 3.32.
\item The unit morphism $R → \utC(A,A)$ is given by the morphism of vertical bicomplexes sending
$1 ∈ R$ to $1_A : A → A$, the strict morphism of twisted complexes given by the identity of $A$.
\end{enumerate}
\end{defin}

Definition 4.24
\begin{defin}\label{ubgMod}
We denote by $\ubgMod$ the $\bgmod$-enriched category of bigraded modules given
by the following data.

\begin{enumerate}[(1)]
\item The objects of $\ubgMod$ are bigraded modules.
\item For $A,B$ bigraded modules the hom-object is the bigraded module $\ubgMod(A,B)$.
\item The composition morphism $c : \ubgMod(B,C) ⊗ \ubgMod(A,B) → \ubgMod(A,C)$ is given by
Definition 3.32.
\item The unit morphism $R → \ubgMod(A,A)$ is given by the morphism of bigraded modules that
sends $1 ∈ R$ to $1_A : A → A$, the strict morphism given by the identity of $A$.
\end{enumerate}
\end{defin}

This next tensor corresponds to $\underline{\otimes}$ in the categorical set up.

Lemma 4.27
\begin{defin}\label{tensorenriched}
The monoidal structure of $\utC$ is given by the following map of vertical bicomplexes.
\[\widehat{⊗}: \utC(A,B) ⊗ \utC(A′,B′) → \utC(A ⊗ A′,B ⊗ B′)\]
\[(f, g) → (f\widehat{⊗}g)_m :=\sum_{i+j=m}(−1)^{ij}f_i ⊗ g_j\]
The monoidal structure of $\ubgMod$ is given by the restriction of this map.
\end{defin}


 Find a concetual explanation for that tensor product or at least see why it is necessary to satisfy the axioms of monoidal category. Also check whether the restriction to bgMod gives the signs of the composition map on that bigraded module, because that is what Sarah said

Definition 4.28

\begin{defin}\label{ufMod}
The $\bgmod$-enriched category of filtered modules $\ufMod$ is the enriched category
given by the following data.
\begin{enumerate}[(1)]
\item The objects of $\ufMod$ are filtered modules.
\item For filtered modules $(K, F)$ and $(L, F)$, the bigraded module $\ufMod(K,L)$ is given by
\[\ufMod(K,L)^v_u :=\{f : K → L\mid f(F_qK^m) ⊂ F_{q+u}L^{m+v−u}, ∀m, q ∈ \Z\}.\]
\item The composition morphism is given by $c(f, g) = (−1)^{u|g|}fg$, where $f$ has bidegree $(u, v)$.
\item The unit morphism is given by the map $R → \ufMod(K,K)$ given by $1 → 1_K$.
\end{enumerate}
\end{defin}

Definition 4.31
\begin{defin}\label{fmoddifferential}
Let $(K, d^K, F)$ and $(L, d^L, F)$ be filtered complexes. We define $\ufC(K,L)$ to be the
vertical bicomplex whose underlying bigraded module is $\ufMod(K,L)$ with vertical differential
\[δ(f) := c(d^L, f) − (−1)^{\langle f,d^K\rangle}c(f, d^K) = d^Lf − (−1)^{v+u}fd^K = d^Lf − (−1)^{|f|}fd^K\]
for $f ∈ \ufMod(K,L)^v_u$. Composition from $\ufMod$.
\end{defin}

Definition 4.33
\begin{defin}\label{ufC}
The $\vbc$-enriched category of filtered complexes $\ufC$ is the enriched category given
by the following data.
\begin{enumerate}[(1)]
\item The objects of $\ufC$ are filtered complexes.
\item For $K,L$ filtered complexes the hom-object is the vertical bicomplex $\ufC(K,L)$.
\item The composition morphism is given as in $\ufMod$ in Definition 4.28 
\item The unit morphism is given by the map $R → \ufC(K,K)$ given by $1 → 1_K$.
We denote by $\usfC$ the full subcategory of $\ufC$ whose objects are split filtered complexes.

\end{enumerate}
\end{defin}

Lemma 4.36
\begin{defin}\label{tensorenriched2}
The monoidal structure of fMod R is given by the following map of vertical bicomplexes.
\[\widehat{⊗}: \ufC(K,L) ⊗ \ufC(K′,L′) → \ufC(K ⊗ K′,L ⊗ L′),\]
\[(f, g) → f\widehat{⊗}g := (−1)^{u|g|}f ⊗ g\]
where $f$ has bidegree $(u, v)$.
\end{defin}
 Again see how the signs do their job

Definition 4.38
\begin{defin}\label{enrichedtot}
Let $A,B$ be bigraded modules and $f ∈ \ubgMod (A,B)^v_u$ we define
\[\Tot(f) ∈ \ufMod(\Tot(A),\Tot(B))^v_u\]
to be given on any $a ∈ \Tot(A)^n$ by
\[(\Tot(f)(a))){j+u} :=
\sum_{m≥0}(−1)^{(m+u)n}f_m(a_{j+m}) ∈ B^{j+n+v}_{j+u} ⊂ \Tot(B)^{n+v−u}.\]
Let $K = \Tot(A)$, $L = \Tot(B)$ and $g ∈ \ufMod(K,L)^v_u$ we define
\[f := \Tot^{−1}(g) ∈ \ubgMod(A,B)^v_u\]
to be $f := (f_0, f_1,\dots)$ where $f_i$ is given on each $A^{m+j}_j$ by the composite
\begin{align*}
f_i : A^{m+j}_j \hookrightarrow\prod_{k≤j}A^{m+k}_k = F_j(\Tot(A)^m)\xrightarrow{g}&F_{j+u}(\Tot(B)^{m+v−u})\\
&=\prod_{l≤j+u}B^{m+v−u+l}_l\xrightarrow{×(−1)^{(i+u)m}} B^{m+j+v−i}_{j+u−i} ,
\end{align*}
where the last map is a projection and multiplication with the indicated sign.
\end{defin} 


Tot comes with column filtration, so recall that (It wouldn't hurt to filter my modules with the column filtration).  Tot being monoidal over a bigradaded category implies that the source and target categories must be enriched accordingly over the same category (see also Lemma  4.37)

Definition 4.42 for the weird End (Example 4.44 as well)

Definitionn 4.49 for Ainfty morphism of twisted complexes. Later, before 4.50 they say Ainfty algebra in twisted complex, I understand this means the Ainfty multiplications are morphisms in the category, but exactly which one (like, some enrichment, the same as in def 4.49?) IN THE ENRICHED CATEGORY SO A BETTER NOTATION WOULD USE THE CALIGRAPHIC UNDERLINED TC


\section{Results}
If the results need previous definitions or results that I haven't included, indicate it and add them (even if they're above it might be useful to refer to the definitions)


Theorem 3.8 with the previous definitions of Tot and d on morphisms

Theorem 3.11, remark that forgetting about the filtration the result is still true

Lemma 4.37, maybe the filtratioon can be omitted as in Theorem 3.11. This one needs Proposition 3.11 but also some theory that I have skipped for now

Theorem 4.39, checking this proof might shed some light onto why we need filtrations to extend Tot to any bidegree

Proposition 4.46 which uses the categorical machinery, I would like to know how the enriched functor things works for instance if we are working with twisted complexes (so that the weird End is as in Example 4.44). In the case of totalization, how can you enrich source and target to have the same enrichment whhen Tot always goes from bigraded to graded: $\ufC$ and $\utC$ both are enriched over $\vbc$, thanks to the filtration, since it gives $\ufMod$ (and thus $\ufC$) the extra grading

Propositioon 4.47. A very important one that I have checed before, but may check again in more detail after understanding monoidal structures. Should clear what $\mathrm{End}_A$ is in this theorem. Since it is in $\vbc$ it should come with some of the enrichment (the one giving it a vertical diferential), that should be more clear SINCE WE ARE IMPOSING MU GOES TO DA IT DOESNT MATTER

Theorem 4.50? May be useful

NEXT SECTION 4.6, IT STARTS WITH THE ASSERTION OF AN ISOMORPHISM THAT I HAVE TO FIND OR CHECK (thorem 4.39 even in the non bounded case, but I guess they want strong monoidality here)

Lemma 4.54: the isomorphisms is in the bounded case, but with compact support I think it should always work (go back to the definitions and results used, but I think I did that once and arrived to the same conclusion) TOTALIZATION WITH COMPACT SUPPORT IS NOT USEFUL FOR TWISTED COMPLEXES BEECAUSE IN GENERAR  THERE ARE INFINETLY MANY NONZERO DIFFERENTIALS, SO WHEN DEFINING THE DIFFERENTIAL IN TOTALIZATION IT WOULDNT BE WELL DEFINED. AND DIRECT PRODUCT TOTALIZATION IS NOT USED EITHER BECAUSE OF WHAT IS SAID BELOW DEF 3.7, WE NEED THE COORDINATES TO BE 0 AT SOME POINT

PROPOSITION 4.11 FIRST PART OF THE PROOF IN SOME ESPECIFIC CASE (IDEALLY ONE OF THE PAPER)?
Regarding the framework, at the begining they say that all the assumptions will hold, but actually they do define external tensor products and the mooidal structures, I understan that this is to check that it actually holds (in addition to show how it holds) Is the hat tensor the same thing as the underlined tensor? YES

Proposition 4.40

Proposition 4.55 WHY SYMMETRIC MONOIDALITY OF TOT IMPLIES THAT ABOUT THE DIFFERENTIAL, WHICH IS THE DIFERENTIAL ON THE ENRICHED END AS FILTERED COMPLEX (ALSO SEE HOW THE N,Z BIGRADING IS NECESSARY FOR THESE PROPERTIES), I DON'T FULLY UNDERSTAND LAST PARAGRAPH, WHAT HAPPENS IF WE FORGET ABOUT FILTRATIONS HERE? ARE THERE MORE AINFTY STRUCTURES ON TOT(A)?
\end{document}
